Automated neuroimaging data-management with Sea

### 2022-05-10 paper/sea-neuro/paper-neuro.tex
reorganized text and resized figures
Comments in intro

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

    The recent explosion in publicly available neuroimaging data has lead to new data
    management challenges, from storage infrastructure application processing times. To meet the storage, accessibility and
    security demands of neuroimaging data, large datasets have been stored in object stores provided by cloud storage providers.
    Standardized metadata formats, such as the Brain Imaging Data Standards (BIDS)\cite{bids}, have been implemented to facilitate the sharing
    of the datasets. Tools such as DataLad~\cite{datalad} have been developed to provide versioning and provenance capture of data.
    Furthermore, recent developments in neuroimaging pipelines have addressed computation time limitations by adopting machine-learning approaches.
    While all these solutions to Big Data-related data management exist, certain aspects, such as processing-related data-transfer overheads
    have received limited attention.

@@

    Newer neuroimaging applications leveraging popular neuroimaging pipeline engines
    also do not benefit from processing-related data management.
    Although engines such as Nipype~\cite{nipype} and
    Joblib~\cite{joblib} do not prohibit the use of data-management
    strategies, they do not facilitate the integration of these strategies into their resulting workflow. To give
    neuroimaging applications data management capabilities, the applications
    must interact with a file system or library that enable the strategies.

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}

\newcommand{\TG}[1]{\color{red}\textsc{From Tristan}: #1\xspace\color{black}}

@@

    The recent explosion in publicly available neuroimaging data has lead to new data
    management challenges, from storage infrastructure application processing times \TG{missing word?}. To meet the storage, accessibility and
    security demands of neuroimaging data, large datasets have been stored in object stores provided by cloud storage providers \TG{mentioning clouds so early in the paper may give the impression that the paper will focus on them.}.
    Standardized metadata formats, such as the Brain Imaging Data Standards (BIDS)\cite{bids}, have been implemented to facilitate the sharing
    of the datasets. Tools such as DataLad~\cite{datalad} have been developed to provide versioning and provenance capture of data.
    Furthermore, recent developments in neuroimaging pipelines have addressed computation time limitations by adopting machine-learning approaches \TG{cite fastsurfer, hd-bet}.
    While all these solutions to Big Data-related data management exist, certain aspects, such as processing-related data-transfer overheads
    have received limited attention.

@@

    Newer neuroimaging applications leveraging popular neuroimaging pipeline engines
    also do not benefit from processing-related data management.
    Although engines such as Nipype~\cite{nipype} and
    Joblib~\cite{joblib} \TG{joblib is multithreading, dask or ray. I wouldn't call it an engine. You should use another example.} do not prohibit the use of data-management
    strategies, they do not facilitate the integration of these strategies into their resulting workflow. To give
    neuroimaging applications data management capabilities, the applications
    must interact with a file system or library that enable the strategies.
